Equivalent Income Outcome Visualisation - Batch out

### 2024-01-05 minos/outcomes/equivalent_income_out_batch.Rmd
Forgot to track the script...

```{r}
# S7.var.list <- c('hh_income', 'equivalent_income',  # Income variables
#                  'S7_housing_quality', 'S7_neighbourhood_safety', 'S7_physical_health', 'S7_mental_health', 'S7_labour_state', 'loneliness',  # SIPHER 7 variables
#                  'ethnicity', 'age', 'region', 'job_sec', 'education_state', 'nkids_ind', 'housing_tenure', 'urban')
# out.path.batch <- here::here('output', 'SIPHER7_batch/')
# 
# base.batch <- read_batch_out_all_years(out.path.batch, 'baseline', start.year = 2021, var.list = S7.var.list, verbose=FALSE)
# wage.batch <- read_batch_out_all_years(out.path.batch, 'livingWageIntervention', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=FALSE)
# energy.batch <- read_batch_out_all_years(out.path.batch, 'energyDownlift', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=FALSE)
# child.batch <- read_batch_out_all_years(out.path.batch, 'hhIncomeChildUplift', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=FALSE)
# pov.batch <- read_batch_out_all_years(out.path.batch, 'hhIncomePovertyLineChildUplift', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=FALSE)

out.path.arc <- here::here('output', 'SIPHER7_batch_ARC/')

base.batch <- read.csv(paste0(out.path.arc, 'baseline_batch_aggregated.csv'))
wage.batch <- read.csv(paste0(out.path.arc, 'wage_batch_aggregated.csv'))
energy.batch <- read.csv(paste0(out.path.arc, 'energy_batch_aggregated.csv'))
child.batch <- read.csv(paste0(out.path.arc, 'child_batch_aggregated.csv'))
pov.batch <- read.csv(paste0(out.path.arc, 'pov_batch_aggregated.csv'))
```

>>>>

```{r}
S7.var.list <- c('hh_income', 'equivalent_income',  # Income variables
                 'S7_housing_quality', 'S7_neighbourhood_safety', 'S7_physical_health', 'S7_mental_health', 'S7_labour_state', 'loneliness',  # SIPHER 7 variables
                 'ethnicity', 'age', 'region', 'job_sec', 'education_state', 'nkids_ind', 'housing_tenure', 'urban')
out.path.batch <- here::here('output', 'SIPHER7/')

base.batch <- read_batch_out_all_years(out.path.batch, 'baseline', start.year = 2021, var.list = S7.var.list, verbose=FALSE)
wage.batch <- read_batch_out_all_years(out.path.batch, 'livingWageIntervention', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=FALSE)
energy.batch <- read_batch_out_all_years(out.path.batch, 'energyDownlift', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=FALSE)
child.batch <- read_batch_out_all_years(out.path.batch, 'hhIncomeChildUplift', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=FALSE)
pov.batch <- read_batch_out_all_years(out.path.batch, 'hhIncomePovertyLineChildUplift', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=FALSE)

# out.path.arc <- here::here('output', 'SIPHER7_batch_ARC/')
# 
# base.batch <- read.csv(paste0(out.path.arc, 'baseline_batch_aggregated.csv'))
# wage.batch <- read.csv(paste0(out.path.arc, 'wage_batch_aggregated.csv'))
# energy.batch <- read.csv(paste0(out.path.arc, 'energy_batch_aggregated.csv'))
# child.batch <- read.csv(paste0(out.path.arc, 'child_batch_aggregated.csv'))
# pov.batch <- read.csv(paste0(out.path.arc, 'pov_batch_aggregated.csv'))
```
